---
title: "Merck Curiosity Paper - Country Comparison Results"
author: "Patrick E. McKnight and Todd B. Kashdan"
format: 
  html:
    toc: true
    toc-location: left
    toc_depth: 3
    html-math-method: katex

theme: cosmo 
---

<!--- Hello source code reader!  This is a quarto file.  It is a markdown file with embedded R code.  The R code is executed and the results are displayed in the document.  The R code is executed in the order in which it appears in the document.  Come peruse the code and the results.  If you have any questions, please contact Patrick McKnight via email (gmu is fine).  Thanks for your interest in our work.  -->

# Merck Curiosity Paper - Country Comparison Results


```{r load libraries, include=FALSE}
#| echo: false
#| results: hide
#| warning: false
#| message: false
#| error: true
#| cache: true

# load all libraries here
library(tidyverse)
library(lavaan)
library(psych)
library(semPlot)
library(GPArotation)
library(ggcorrplot)
library(knitr)
library(kableExtra)
library(apaTables)
library(xlsx)
library(digest)

```



# Data Source

Data delivered directly from Merck in a password protected MS Excel (xlsx) file (Merck Curiosity Survey_Data_PWD.xlsx). The mdsum hash of the original xlsx file:

```{r}
cat("md5sum 7734c8a6659f0460653bd52b85c456cf Merck Curiosity Survey_Data_PWD.xlsx")
```

The original xlsx file was converted to a csv file (Merck_Curiosity_Survey_Data_NO_PWD.csv) using the following R code:

```{r convert xlsx to csv, include=FALSE}
#| echo: false
#| results: hide
#| warning: false
#| message: false
#| error: false
#| cache: true
#| fig.cap: "md5 hash of the data"

# read a xlsx file with a password and save to a data frame
library(xlsx)
library(digest)

# run the following code if a file does not exist in the current directory
if (!file.exists("Merck_Curiosity_Survey_Data_NO_PWD.csv")) { # convert xlsx to csv BEGIN
  # read a xlsx file with a password and save to a data frame
  df <- xlsx::read.xlsx("Merck_Curiosity_Survey_Data_PWD.xlsx", 
                        sheetIndex = 1, 
                        password = "*dke5!rUUnyz2&L")
  # remove the first row (variable names)
  df.fin <- df[-1,]
  # save the variable names
  df.varnames <- df[1,]
   
  # convert columns 2 through 17 from chr to numeric
  df.fin[,2:17] <- sapply(df.fin[,2:17], as.numeric)
  df.fin[,18:38] <- sapply(df.fin[,18:38], as.numeric)
   
  df.fin$Locale <- as.factor(df.fin$Country.of.Subsidiary)
   
  # save df.fin to a csv file
  write.csv(df.fin, file = "Merck_Curiosity_Survey_Data_NO_PWD.csv", row.names = FALSE)
   
  # save df.varnames to a csv file
  write.csv(as.data.frame(t(df.varnames)),
             file="Merck_Curiosity_Survey_Data_NO_PWD_varnames.csv",
             row.names = TRUE)
} # convert xlsx to csv END

# # read a xlsx file with a password and save to a data frame
# df <- xlsx::read.xlsx("Merck Curiosity Survey_Data_PWD.xlsx", sheetIndex = 1, password = "*dke5!rUUnyz2&L")
# # remove the first row (variable names)
# df.fin <- df[-1,]
# # save the variable names
# df.varnames <- df[1,]
# 
# # convert columns 2 through 17 from chr to numeric
# df.fin[,2:17] <- sapply(df.fin[,2:17], as.numeric)
# df.fin[,18:38] <- sapply(df.fin[,18:38], as.numeric)
# 
# df.fin$Locale <- as.factor(df.fin$Country.of.Subsidiary)
# 
# # save df.fin to a csv file
#write.csv(df.fin, file = "Merck_Curiosity_Survey_Data_NO_PWD.csv", row.names = FALSE)
#write.csv(df.varnames, file = "Merck_Curiosity_Survey_Data_NO_PWD_varnames.csv", row.names = TRUE)

df.fin <- read.csv("Merck_Curiosity_Survey_Data_NO_PWD.csv", header = TRUE)

# read the variable names
df.varnames <- read.csv("Merck_Curiosity_Survey_Data_NO_PWD_varnames.csv", header = TRUE)
# print df.varnames with row.names
df.varnames

# get the md5 hash of the data frame
#md5 <- digest(df, algo = "md5")
# print the md5 hash
#print(md5)

```

## Checking the data integrity

The original file

md5sum 7734c8a6659f0460653bd52b85c456cf Merck Curiosity Survey_Data_PWD.xlsx

## Data Description

```{r}
#| echo: false
#| results: hide
#| warning: false
#| message: false
#| error: false
#| cache: true

# print the data frame
df.fin

# print the variable names
names(df.fin)
```

## Descriptive Statistics

```{r}
#| echo: false
#| 

# descriptive statistics
library(psych)
describe(df.fin)

# descriptive statistics by country
library(psych)
describeBy(df.fin, group = df.fin$Locale)

```


# Data Analysis

## Data Analysis Plan

The data analysis plan was developed by Patrick E. McKnight and Todd B. Kashdan. The data analysis plan was reviewed and approved by Merck prior to data analysis.

## Data Analysis

```{r}
#| echo: false

# load the data
df.fin <- read.csv("Merck_Curiosity_Survey_Data_NO_PWD.csv", header = TRUE)

# load the variable names
df.varnames <- read.csv("Merck_Curiosity_Survey_Data_NO_PWD_varnames.csv", header = TRUE)

# load the packages
library(psych)
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(ggcorrplot)
library(gridExtra)
library(grid)
library(reshape2)
library(dplyr)
library(corrplot)
library(Hmisc)
library(ggcorrplot)
library(ggExtra)
library(ggpubr)

# convert the Locale variable to a factor
df.fin$Locale <- as.factor(df.fin$Locale)


```

