---
title: "Merck Curiosity Paper - Country Comparison Results"
author: "Kashdan and McKnight"
format: html
---

## Data

We got this data directly from Merck in a password protected xlsx file (Merck Curiosity Survey_Data_PWD.xlsx).  The mdsum hash is:

```{r}
#| echo: false
#| results: hide
#| warning: false
#| message: false
#| error: false
#| cache: false
#| fig.cap: "md5 hash of the data"


# read a xlsx file with a password and save to a data frame
#library(xlsx)
#library(digest)


# run the following code if a file does not exist in the current directory
# if (!file.exists("Merck_Curiosity_Survey_Data_NO_PWD.csv")) {
#   # read a xlsx file with a password and save to a data frame
#   df <- xlsx::read.xlsx("Merck_Curiosity_Survey_Data_PWD.xlsx", sheetIndex = 1, password = "*dke5!rUUnyz2&L")
#   # remove the first row (variable names)
#   df.fin <- df[-1,]
#   # save the variable names
#   df.varnames <- df[1,]
#   
#   # convert columns 2 through 17 from chr to numeric
#   df.fin[,2:17] <- sapply(df.fin[,2:17], as.numeric)
#   df.fin[,18:38] <- sapply(df.fin[,18:38], as.numeric)
#   
#   df.fin$Locale <- as.factor(df.fin$Country.of.Subsidiary)
#   
#   # save df.fin to a csv file
#   write.csv(df.fin, file = "Merck_Curiosity_Survey_Data_NO_PWD.csv", row.names = FALSE)
#   
#   # save df.varnames to a csv file
  # write.csv(as.data.frame(t(df.varnames)),
  #            file="Merck_Curiosity_Survey_Data_NO_PWD_varnames.csv",
  #            row.names = FALSE)
# }

# # read a xlsx file with a password and save to a data frame
# df <- xlsx::read.xlsx("Merck Curiosity Survey_Data_PWD.xlsx", sheetIndex = 1, password = "*dke5!rUUnyz2&L")
# # remove the first row (variable names)
# df.fin <- df[-1,]
# # save the variable names
# df.varnames <- df[1,]
# 
# # convert columns 2 through 17 from chr to numeric
# df.fin[,2:17] <- sapply(df.fin[,2:17], as.numeric)
# df.fin[,18:38] <- sapply(df.fin[,18:38], as.numeric)
# 
# df.fin$Locale <- as.factor(df.fin$Country.of.Subsidiary)
# 
# # save df.fin to a csv file
# write.csv(df.fin, file = "Merck Curiosity Survey_Data_NO_PWD.csv", row.names = FALSE)

df.fin <- read.csv("Merck_Curiosity_Survey_Data_NO_PWD.csv", header = TRUE)

# read the variable names
df.varnames <- read.csv("Merck_Curiosity_Survey_Data_NO_PWD_varnames.csv", header = TRUE)
# print df.varnames with row.names
print(df.varnames, row.names = T)

# get the md5 hash of the data frame
#md5 <- digest(df, algo = "md5")
# print the md5 hash
#print(md5)

```

## Checking the data integrity

The original file 

md5sum 7734c8a6659f0460653bd52b85c456cf  Merck Curiosity Survey_Data_PWD.xlsx



## Data Description




## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this 

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
